Supplementary Information

### 2021-06-03 doc/manuscript/ForestGEO_treerings.Rmd
author/inst edits

[Kristina J. Anderson-Teixeira](0000-0001-8461-9713)^1,2^*,
Valentine Herrmann^1^,
Christy Rollinson^3^,
Bianca Gonzalez^1^,
Erika B. Gonzalez-Akre^1^,
Neil Pederson^4^,
[M. Ross Alexander](0000-0003-1106-1100)^5^**,
Craig D. Allen^6^,
Raquel Alfaro-Sánchez^7^,
Tala Awada^8^,
Jennifer L. Baltzer^7^,
Patrick J. Baker^9^,
[Joseph D. Birch](0000-0001-8644-7345)^10^,
Sarayudh Bunyavejchewin^11^,
Paolo Cherubini^12,13^,
Stuart J. Davies^2^,
Cameron Dow^1,14^,
Ryan Helcoski^1^,
[Jakub Kašpar](0000-0003-1780-6310)^15^,
[James Lutz]( 0000-0002-2560-0710)^16^,
Ellis Q. Margolis^17^,
Justin Maxwell^18^,
Sean McMahon^2,19^,
Camille Piponiot^1,2,20^,
Sabrina E. Russo^21,22^,
[Pavel Šamonil](0000-0002-7722-8797)^15^,
Anastasia E. Sniderhan^7^,
[Alan J. Tepley](0000-0002-5701-9613)^1,23^,
[Ivana Vašíčková](0000-0002-6070-5956)^15^, 
Mart Vlam^24^,
Pieter A. Zuidema^24^

@@

3. The Morton Arboretum, Center for Tree Science, Lisle, Illinois 60532 USA

>>>>

[Kristina J. Anderson-Teixeira](0000-0001-8461-9713)^1,2^*,
Valentine Herrmann^1^,
Christine R. Rollinson^3^,
Bianca Gonzalez^1^,
Erika B. Gonzalez-Akre^1^,
Neil Pederson^4^,
[M. Ross Alexander](0000-0003-1106-1100)^5^**,
Craig D. Allen^6^,
Raquel Alfaro-Sánchez^7^,
Tala Awada^8^,
Jennifer L. Baltzer^7^,
Patrick J. Baker^9^,
[Joseph D. Birch](0000-0001-8644-7345)^10^,
Sarayudh Bunyavejchewin^11^,
Paolo Cherubini^12,13^,
Stuart J. Davies^2^,
Cameron Dow^1,14^,
Ryan Helcoski^1^,
[Jakub Kašpar](0000-0003-1780-6310)^15^,
[James A. Lutz]( 0000-0002-2560-0710)^16^,
Ellis Q. Margolis^17^,
Justin Maxwell^18^,
Sean McMahon^2,19^,
Camille Piponiot^1,2,20^,
Sabrina E. Russo^21,22^,
[Pavel Šamonil](0000-0002-7722-8797)^15^,
Anastasia E. Sniderhan^7^,
[Alan J. Tepley](0000-0002-5701-9613)^1,23^,
[Ivana Vašíčková](0000-0002-6070-5956)^15^, 
Mart Vlam^24^,
Pieter A. Zuidema^24^

@@

3. Center for Tree Science, The Morton Arboretum, Lisle, Illinois 60532 USA
